### 2020-01-31 wuhan.tex

Consistent with our previous observations (\fref{eff}),
we find that accounting for uncertainties in the estimate of $r$ has the largest effect on the estimates of \Ro (\fref{R0}).
For example, recalculating \Ro for Study 6 by using our pooled estimate of $r$ gives $\mathcal R_0 = 3.9$ (95\% CI: 2.3--9.8), which is much wider than the range they reported (2.0--3.1).
There are two explanations for this result.
First, even though the exponential growth rate $r$ and the mean generation time $\bar G$ have identical effects on \Ro under the gamma approximation framework \eref{gamma},
$r$ has a greater overall effect on \Ro because it is associated with more uncertainty (\fref{assumption}).
%% \jd{I am less against these words, although I don't love having them. But we would need a bit more precision (easiest would be to report >2.4, < 1.6 or something (I made the specific numbers up).
%% the range of the 95\% confidence interval on $\mu_r$ spans over more than a two-fold difference, whereas the range of the 95\% confidence intervals on $\mu_G$ does not.
Second, assuming a fixed generation time ($\kappa=0$) makes the estimate of \Ro too sensitive to $r$ and $\bar G$ as discussed previously.

>>>>

Consistent with our previous observations (\fref{eff}),
we find that accounting for uncertainties in the estimate of $r$ has the largest effect on the estimates of \Ro (\fref{R0}).
For example, recalculating \Ro for Study 6 by using our pooled estimate of $r$ gives $\mathcal R_0 = 3.9$ (95\% CI: 2.3--9.8), which is much wider than the range they reported (2.0--3.1).
There are two explanations for this result.
First, even though the exponential growth rate $r$ and the mean generation time $\bar G$ have identical effects on \Ro under the gamma approximation framework (\eref{gamma} in Methods),
$r$ has a greater overall effect on \Ro because it is associated with more uncertainty (\fref{assumption}).
%% \jd{I am less against these words, although I don't love having them. But we would need a bit more precision (easiest would be to report >2.4, < 1.6 or something (I made the specific numbers up).
%% the range of the 95\% confidence interval on $\mu_r$ spans over more than a two-fold difference, whereas the range of the 95\% confidence intervals on $\mu_G$ does not.
Second, assuming a fixed generation time ($\kappa=0$) makes the estimate of \Ro too sensitive to $r$ and $\bar G$ as discussed previously.
